PInSoRo: A Dataset for Deep-learning of Human-Robot Social Interactions

### 2017-06-23 paper.tex
More on the dataset structure

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{3d-point-cloud-facial-features}
    \caption{The freeplay sandbox, viewed at runtime within ROS RViz. The
    current background drawing (bottom left) is published on a regular image
    topic. Simple computer vision is used to segment it into zones (visible in
    the central panel). The poses and bounding boxes of the interactive items
    are published as well, and turned into an occupancy map, used to plan the
    robot's arm motion.
    visualisation tool.}
    \label{fig|rviz}
\end{figure}

@@

The dataset consists in a collection of records. Each record correspond to one
play interaction between two children. To date (June 2017) \todo[inline]{put
latest nb} records have been acquired. At the end of the acquisition campaign
(July 2017), the dataset is planned to include 50 records (\ie 100 children). As
mentioned above, the duration of each play episode varies ($M=17m13s,
SD=8m02s$), but it is capped to a maximum of 40 minutes.

@@

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{3d-point-cloud-facial-features}
    \caption{Reconstructed 3D point cloud with 68 facial features high-lighted}
    \label{fig|pointcloud}
\end{figure}

@@

The dataset consists in a collection of records. Each record correspond to one
play interaction between two children. To date (June 2017) 19 records have been acquired. At the end of the acquisition campaign
(July 2017), the dataset is planned to include 50 records (\ie 100 children). As
mentioned above, the duration of each play episode varies ($M=17m13s,
SD=8m02s$), but it is capped to a maximum of 40 minutes.

\todo[inline]{update with last nb before submitting}

Data is collected using the ROS middleware\footnote{\url{http://ros.org}} and
recorded as \emph{bag} files. Every dataframe is timestamped.
Table~\ref{table|datastreams} lists all the recorded datastreams.

@@

As the data is recorded using ROS's bag files, it can be replayed in the exact
same conditions as it was during the recording. All the video streams use
calibrated cameras. While the raw RGB and depth streams are neither rectified
nor registered together (due to performance considerations during the
recording), it can be easily achieved as a post-process step, using standard ROS
tools (the ROS {\tt rgbd\_pipeline}). Pre-configured scripts are available
alongside the
dataset\footnote{Available online from
\url{https://github.com/severin-lemaignan/freeplay-sandbox-analysis}.} to
republish registered streams and the corresponding 3D point-clouds (as seen in
Figure~\ref{fig|pointcloud}).
